Comment: Inferring Trade Costs from Trade Booms and Trade Busts

### 2017-09-26 Paper/Manuscript.tex
Update Manuscript.tex

\begin{abstract}
\cite{JMN2011} offer a method to measure trade costs that relies exclusively on bilateral exports and GDP statistics.
They argue that the reduction in trade costs was the main driving force of trade growth during the first globalization (1870-1913), whereas economic expansion was the main driving force during the second globalization (1950-2000).
This potentially major result is driven by the use of an \textit{ad hoc} aggregation method of bilateral trade costs to the country and global level.
What \cite{JMN2011} capture is the difference in the relative starting trade of dyads experiencing faster trade growth in the first and second globalization.
More generally, we cast doubts on the possibility to reach conclusions on aggregate costs with a method that excludes \textit{a priori} changes in non-trade costs determinants of openness rates and hence can only rephrase the information contained in them.
\end{abstract}

@@

Jacks, Meissner and Novy's method for inferring trade costs
from trade flows simply reformulates the evolution of the
openness ratio when it is used to calculate aggregate trade
costs. This is because it only relates the two through an
equality between MRS and price ratio. It appears more clearly
when comparing the \textit{ad hoc} aggregation of bilateral trade costs
to an aggregated measure of trade costs based on
\cite{AW2003}'s model. Still, if their method fails to offer a
full alternative to traditional investigations of trade costs,
such as commodity price gaps, it provides an improvement in the
microfoundation of gravity equations by substantially
simplifying the way of correcting the omitted variable bias.

This characteristic of the proposed measure of trade costs is
partly due to the all-inclusive definition of trade
costs used by the authors. In such a model, costs are anything
that causes consumptions from different countries' products not
to be equal. To be sure, it is essential to highlight that
trade costs cannot be reduced to tariffs or transportation
costs, and to insist on the need for a quantification of all
the impediments to international trade. But the concept of
trade costs loses part of its interest if there are no causal
alternatives to explain changing trade patterns. Such a definition is
therefore bound to reword the information given by trade
flows relative to output, such as contained in an openness
ratio.

>>>>

\begin{abstract}
\cite{JMN2011} offer a method to measure trade costs that relies exclusively on bilateral exports and GDP statistics.
They argue that the reduction in trade costs was the main driving force of trade growth during the first globalization (1870-1913), whereas economic expansion was the main driving force during the second globalization (1950-2000).
This potentially major result is driven by the use of an \textit{ad hoc} aggregation method of bilateral trade costs at the country and at the global levels.
What \cite{JMN2011} capture is the difference in the relative starting trade of dyads experiencing faster trade growth in the first and second globalization.
More generally, we cast doubts on the possibility to reach conclusions on aggregate costs with a method that excludes \textit{a priori} changes in non-trade costs determinants of openness rates and hence can only rephrase the information contained in them.
\end{abstract}

@@

Jacks, Meissner and Novy's method for inferring trade costs
from trade flows simply reformulates the evolution of the
openness ratio when it is used to calculate aggregate trade
costs. Namely it only relates the two through an
equality between the MRS and the price ratio. It appears more clearly
when comparing the \textit{ad hoc} aggregation of bilateral trade costs
to an aggregated measure of trade costs based on
\cite{AW2003}'s model. Still, if their method fails to offer a
full alternative to traditional investigations of trade costs,
such as commodity price gaps, it provides an improvement in the
microfoundation of gravity equations by substantially
simplifying the way of correcting the omitted variable bias.

This characteristic of the proposed measure of trade costs is
partly due to the all-inclusive definition of trade
costs used by the authors. In such a model, costs are anything
that causes consumption flows from different countries' products not
to be equal. Yet it is essential to highlight that
trade costs cannot be reduced to tariffs or transportation
costs, and to insist on the need for a quantification of all
the impediments to international trade. But the concept of
trade costs loses part of its interest if there are no causal
alternatives to explain changing trade patterns. Such a definition is
therefore bound to reword the information given by trade
flows relative to output, such as contained in an openness
ratio.
